Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-03 draft/draft.tex
progress

Consider a set of $N=n+1$ teams labeled by $\{0,1,...,n\}$ to be rated and ranked.
For this aim, assume that some set of pairwise comparison scores $\psi_{ij}=-\psi_{ji}$ is provided for each $ij$ of different labels $i$ and $j$.
Informally, the score $\psi_{ij}$ should be positive if the pairwise comparison indicates that team $i$ should be rated higher than team $j$ and it should be non-positive otherwise.
One way to obtain rating scores somehow consistent with the pairwise comparisons scores, consist in finding ratings $w_i$ for $i=0,1,..,n$ such that minimize the sum of squared differences
$$
\sum_{ij:i<j} |\psi_{ij}-(w_i-w_j)|^2.
$$

>>>>

Consider a set of $N=n+1$ teams labeled by $\{0,1,...,n\}$ to be rated and ranked.
For this aim, assume that some set of pairwise comparison scores $\psi_{ij}=-\psi_{ji}$ is provided for each $ij$ of different labels $i$ and $j$.
Informally, the score $\psi_{ij}$ should be positive if the pairwise comparison indicates that team $i$ should be rated higher than team $j$ and it should be non-positive otherwise.
One way to infer rating scores somehow consistent with the pairwise comparisons scores, consist in finding ratings $w_i$ for $i=0,1,..,n$ that minimize the sum of squared differences
$$
\sum_{ij:i<j} |\psi_{ij}-(w_i-w_j)|^2.
$$
This is a well defined mathematical problem that can be conveniently reformulated in the language of cochains over simplicial complexes.
In fact, this reformulation is known as the HodgeRank method for the inference of ratings and rankings starting from pairwise comparison scores~\cite{jiang2011statistical,
perotti2025analysis}.
